 

### 2021-03-09 doc/manuscript/tables_figures/tables.Rmd
started hypothesis table
#119

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypotheses <- read.csv("hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
hypotheses_table <- subset(hypotheses, select = -c(category, percent.sites, percent.species.site.combinations) ) #drop MAT column, plus columns with sd
kable(hypotheses_table, format = "latex", booktabs = TRUE,  escape = F)%>%

  column_spec(1, width = "12cm") %>%
  column_spec(2, width = "5cm") %>%

  pack_rows("Annual growth is jointly influenced by water, temperature, DBH, and time. ", 1, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Drought limits tree growth, but the response to water is nonlinear.", 3, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Temperature has predominantly negative, nonlinear effects on growth.", 6, 9, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("DBH", 10, 13, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%

  kable_styling(latex_options = c( "hold_position", "repeat header"), protect_latex = T, font_size = 7)

```
